Performing and evaluating graph-based clustering with rOpenScPCA

### 2024-11-12 analyses/hello-clusters/01_perform-evaluate-clustering.Rmd
bump ropenscpca for calculate_stability usage

# Visualize values as a density plot, showing the mean value as a vertical line
ggplot(silhouette_results) +
  aes(x = silhouette_width) +
  geom_density(fill = "lightblue") +
  geom_vline(xintercept = mean_silhouette_width, color = "red", size = 1)
```

@@

# Visualize values as a density plot, showing the mean value as a vertical line
ggplot(purity_results) +
  aes(x = purity) +
  geom_density(fill = "lightblue") +
  geom_vline(xintercept = mean_purity, color = "red", size = 1)
```
This metric shows a relatively high average neighborhood purity, suggesting that neighboring cells tend to belong to the same cluster.

@@

```{r stability, warning=FALSE}
stability_results <- calculate_stability(
  sce,
  cluster_results$cluster, # TODO!!!!! Update once the rOpenScPCA hash is updated in this branch
  seed = params$seed
)

@@

```{r plot stability}
ggplot(stability_results) +
  aes(x = ari) +
  geom_density(fill = "lightblue") +
  geom_rug(color = "red", size = 1)
```

@@

# Now, pass in the same arguments customizing parameters here
stability_results_leiden <- calculate_stability(
  sce,
  cluster_df_leiden$cluster, # TODO!!!!! Update once the rOpenScPCA hash is updated in this branch
  algorithm = "leiden",
  resolution = 0.5,
  nn = 15,
  seed = params$seed
)

>>>>

# Visualize values as a density plot, showing the mean value as a vertical line
ggplot(silhouette_results) +
  aes(x = silhouette_width) +
  geom_density(fill = "lightblue") +
  geom_vline(xintercept = mean_silhouette_width, color = "red", linewidth = 1)
```

@@

# Visualize values as a density plot, showing the mean value as a vertical line
ggplot(purity_results) +
  aes(x = purity) +
  geom_density(fill = "lightblue") +
  geom_vline(xintercept = mean_purity, color = "red", linewidth = 1)
```
This metric shows a relatively high average neighborhood purity, suggesting that neighboring cells tend to belong to the same cluster.

@@

```{r stability, warning=FALSE}
stability_results <- calculate_stability(
  sce,
  cluster_results,
  seed = params$seed
)

@@

```{r plot stability}
ggplot(stability_results) +
  aes(x = ari) +
  geom_density(fill = "lightblue") +
  geom_rug(color = "red", linewidth = 1)
```

@@

# Now, pass in the same arguments customizing parameters here
stability_results_leiden <- calculate_stability(
  sce,
  cluster_df_leiden,
  algorithm = "leiden",
  resolution = 0.5,
  nn = 15,
  seed = params$seed
)
